### 2020-06-04 related.tex
fixed reference

Ezell~\cite{osti_1086655} creates a general understanding of Titan's interconnect failures using an application to stress test Titan's Gemini interconnect.
%
The work by Kumar et al.~\cite{kumar18understanding} analyzes Titan's interconnect faults, errors and congestion events to improve resilience of the interconnects and congestion resolution methods. The results show that the magnitude of interconnect errors is very high with an uneven distribution across different types of links. They also show that congestion is very frequent and bursty.
%
Gupta et al.~\cite{7266836} investigate the spatial and temporal properties of failures on Titan and their impact on resilience mechanisms and the implications for efficient system operation.
%
Gupta et al.~\cite{gupta17failures} also perform a study covering five supercomputers at Oak Ridge National Laboratory, including Titan, that concentrates on developing an understanding of which and how many errors and failures occur in supercomputers over multiple generations and over their years of operation. This work resulted in a lot of lessons learned, including that the mean-time between failures (MTBF) can change drastically and non-monotonically over time.
%
Meneses et al.~\cite{Meneses15Analyzing} analyze the interplay and workload on Titan using failure and job submission logs. The results indicate that failures depend heavily on workload.

>>>>

Ezell~\cite{ezell2013} creates a general understanding of Titan's interconnect failures using an application to stress test Titan's Gemini interconnect.
%
The work by Kumar et al.~\cite{kumar18understanding} analyzes Titan's interconnect faults, errors and congestion events to improve resilience of the interconnects and congestion resolution methods. The results show that the magnitude of interconnect errors is very high with an uneven distribution across different types of links. They also show that congestion is very frequent and bursty.
%
Gupta et al.~\cite{7266836} investigate the spatial and temporal properties of failures on Titan and their impact on resilience mechanisms and the implications for efficient system operation.
%
Gupta et al.~\cite{gupta17failures} also perform a study covering five supercomputers at Oak Ridge National Laboratory, including Titan, that concentrates on developing an understanding of which and how many errors and failures occur in supercomputers over multiple generations and over their years of operation. This work resulted in a lot of lessons learned, including that the mean-time between failures (MTBF) can change drastically and non-monotonically over time.
%
Meneses et al.~\cite{Meneses15Analyzing} analyze the interplay and workload on Titan using failure and job submission logs. The results indicate that failures depend heavily on workload.
